### 2020-08-26 benchmarking/benchmarkingVM/ESS_round1_catquant.tex
results update

% Created by tikzDevice version 0.12.3 on 2020-08-10 13:51:28
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,374.64) --
	(203.52,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,490.17) --
	(  0.00,203.52);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (  0.00,346.12) --
	(232.04,578.16);

\path[draw=drawColor,line width= 0.6pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,518.69) --
	(  0.00,232.04);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (  0.00,317.60) --
	(260.56,578.16);

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] (286.65,578.16) --
	(286.65,547.21) --
	(  0.00,260.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (142.89,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,435.87) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (114.37,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,407.35) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 84.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,378.83) {$4\times$};

\path[draw=drawColor,line width= 1.0pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 94.65,416.78) --
	(103.65,416.78);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.64,409.37) --
	( 99.64,422.22);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.64,413.56) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (186.25,476.46) --
	(190.95,476.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (188.73,475.74) --
	(188.73,477.16);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (188.73,472.43) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (100.21,474.21) --
	(104.27,474.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (102.34,473.61) --
	(102.34,474.79);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (102.34,470.18) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 95.11,416.10) --
	(103.73,416.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 99.87,410.35) --
	( 99.87,420.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 99.87,412.07) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 89.40,387.89) --
	(115.90,387.89);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (106.65,384.62) --
	(106.65,390.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (106.65,384.99) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (193.54,483.66) --
	(195.01,483.66);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.29,483.25) --
	(194.29,484.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.29,480.76) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.24,453.03) --
	(151.45,453.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (148.58,451.65) --
	(148.58,454.32);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (148.58,449.80) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.12,479.26) --
	(197.83,479.26);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.99,477.50) --
	(196.99,480.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.99,475.23) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.36,483.73) --
	(188.58,483.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.98,483.50) --
	(187.98,483.96);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (187.98,479.70) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (138.83,449.81) --
	(142.53,449.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.76,448.18) --
	(140.76,451.31);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (140.76,445.77) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (145.30,448.54) --
	(152.66,448.54);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.31,447.26) --
	(149.31,449.74);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (149.31,445.63) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.59,488.02) --
	(199.40,488.02);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.00,487.58) --
	(199.00,488.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.00,485.12) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.84,422.09) --
	(126.52,422.09);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (122.64,409.09) --
	(122.64,429.99);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.64,418.86) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.62,458.97) --
	(195.24,458.97);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (193.51,454.93) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.66,477.15) --
	(163.23,477.15);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.95,476.14) --
	(162.95,478.11);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (162.95,473.11) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (112.91,421.56) --
	(120.70,421.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (117.17,406.76) --
	(117.17,430.08);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (117.17,417.53) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (124.20,409.98) --
	(134.18,409.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.79,405.95) --
	(129.79,413.35);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (129.79,407.07) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.21,485.10) --
	(197.03,485.10);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.62,484.28) --
	(196.62,485.89);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.62,482.19) {$\kappa$};
\definecolor{drawColor}{RGB}{151,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (129.77,432.05) --
	(140.26,432.05);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (135.68,429.18) --
	(135.68,434.57);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (135.68,428.82) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.99,483.34) --
	(200.70,483.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (199.86,480.63) --
	(199.86,485.72);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.86,479.30) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.36,482.25) --
	(177.58,482.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.47,482.07) --
	(177.47,482.44);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (177.47,478.22) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (133.12,451.72) --
	(147.88,451.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (141.79,449.82) --
	(141.79,453.46);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (141.79,447.69) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (136.74,437.84) --
	(147.60,437.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.88,434.82) --
	(142.88,440.47);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (142.88,434.94) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.27,487.58) --
	(198.98,487.58);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (198.14,487.05) --
	(198.14,488.10);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.14,484.68) {$\kappa$};
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (177.42,460.68) --
	(181.15,460.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.37,456.94) --
	(179.37,463.84);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.37,457.45) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.94,486.46) --
	(184.37,486.46);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.33,482.75) --
	(176.33,489.60);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.33,482.42) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.15,482.18) --
	(197.23,482.18);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (196.69,481.57) --
	(196.69,482.78);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (196.69,478.15) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (153.45,441.52) --
	(161.00,441.52);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (157.57,436.94) --
	(157.57,445.26);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (157.57,437.48) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (179.01,463.73) --
	(184.30,463.73);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (181.82,459.32) --
	(181.82,467.36);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (181.82,460.82) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (208.90,498.16) --
	(211.56,498.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (210.27,495.77) --
	(210.27,500.30);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (210.27,495.25) {$\kappa$};
\definecolor{drawColor}{RGB}{68,68,68}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (191.64,472.51) --
	(197.79,472.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (194.95,470.68) --
	(194.95,474.19);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.95,469.28) {$p$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (174.60,491.62) --
	(178.99,491.62);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.91,490.07) --
	(176.91,493.06);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.91,487.58) {$L$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.25,482.68) --
	(197.61,482.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (197.43,482.27) --
	(197.43,483.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (197.43,478.65) {$r$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (175.17,459.25) --
	(178.40,459.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (176.85,457.81) --
	(176.85,460.59);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (176.85,455.21) {$h$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (173.79,467.29) --
	(192.74,467.29);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (185.37,464.24) --
	(185.37,469.95);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (185.37,464.39) {$\sigma$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.72,501.36) --
	(212.84,501.36);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (212.78,500.78) --
	(212.78,501.94);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (212.78,498.46) {$\kappa$};
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (578.16,578.16);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,338.88);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-25 15:33:04
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}
\usepackage[active,tightpage,psfixbb]{preview}
\PreviewEnvironment{pgfpicture}
\setlength\PreviewBorder{0pt}
\usepackage{amssymb}\begin{document}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (  0.00,368.65) --
	(209.51,578.16);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,492.84) --
	(  0.00,209.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00,342.13) --
	(236.03,578.16);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,519.37) --
	(  0.00,236.03);

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (  0.00,315.60) --
	(262.56,578.16);

\path[draw=drawColor,line width= 0.7pt,line join=round,line cap=round] (283.33,578.16) --
	(283.33,545.89) --
	(  0.00,262.56);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (136.90,342.31) {$\frac{1}{64} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,429.88) {$64\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at (110.38,342.31) {$\frac{1}{16} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 52.75,403.36) {$16\times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 82.20,342.31) {$\frac{1}{4} \times$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.83] at ( 51.92,376.84) {$4\times$};

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 49.80,338.88) -- (239.28,528.36);
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 92.06,411.70) --
	(103.71,411.70);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 98.76,408.30) --
	( 98.76,414.58);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 98.76,408.47) {$p$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (127.75,461.51) --
	(136.14,461.51);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (132.40,460.16) --
	(132.40,462.77);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (132.40,457.48) {$L$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.72,453.05) --
	( 91.82,453.05);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 89.44,452.87) --
	( 89.44,453.23);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 89.44,449.02) {$r$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 86.78,407.42) --
	( 95.88,407.42);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 91.87,400.23) --
	( 91.87,412.63);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 91.87,403.39) {$h$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 53.22,385.02) --
	( 67.16,385.02);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] ( 61.43,375.09) --
	( 61.43,391.53);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at ( 61.43,382.12) {$\sigma$};
\definecolor{drawColor}{RGB}{255,0,109}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.05,459.14) --
	(170.79,459.14);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (170.42,458.74) --
	(170.42,459.52);
\definecolor{drawColor}{RGB}{255,0,109}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (170.42,456.23) {$\kappa$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (195.41,484.07) --
	(203.29,484.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.75,480.26) --
	(199.75,487.25);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (199.75,480.85) {$p$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (175.32,468.85) --
	(182.12,468.85);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (179.02,464.40) --
	(179.02,472.46);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (179.02,464.82) {$L$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (202.56,499.80) --
	(209.12,499.80);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (206.12,496.65) --
	(206.12,502.51);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (206.12,495.77) {$r$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (187.18,479.04) --
	(195.29,479.04);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.66,476.43) --
	(191.66,481.33);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.66,475.00) {$h$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.75,482.46) --
	(204.87,482.46);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (201.64,479.93) --
	(201.64,484.70);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (201.64,479.56) {$\sigma$};
\definecolor{drawColor}{RGB}{253,104,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (207.07,499.42) --
	(214.51,499.42);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (211.15,496.11) --
	(211.15,502.24);
\definecolor{drawColor}{RGB}{253,104,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (211.15,496.51) {$\kappa$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (141.42,439.64) --
	(145.39,439.64);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (143.51,437.79) --
	(143.51,441.33);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (143.51,436.42) {$p$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (171.24,465.61) --
	(175.56,465.61);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (173.52,463.95) --
	(173.52,467.13);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (173.52,461.57) {$L$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (193.84,485.78) --
	(195.64,485.78);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (194.76,485.39) --
	(194.76,486.16);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (194.76,481.74) {$r$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (130.58,426.42) --
	(135.71,426.42);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (133.32,424.17) --
	(133.32,428.43);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (133.32,422.38) {$h$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.34,443.92) --
	(161.79,443.92);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.91,440.58) --
	(156.91,446.77);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (156.91,441.02) {$\sigma$};
\definecolor{drawColor}{RGB}{143,161,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (197.72,485.55) --
	(199.65,485.55);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (198.71,485.16) --
	(198.71,485.94);
\definecolor{drawColor}{RGB}{143,161,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (198.71,482.65) {$\kappa$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.25,461.02) --
	(162.39,461.02);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (160.88,460.40) --
	(160.88,461.62);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (160.88,457.79) {$p$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (162.17,460.73) --
	(166.45,460.73);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (164.43,458.38) --
	(164.43,462.82);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (164.43,456.70) {$L$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (190.93,485.98) --
	(191.45,485.98);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (191.19,485.77) --
	(191.19,486.19);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (191.19,481.95) {$r$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (147.67,456.98) --
	(154.15,456.98);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (151.19,455.19) --
	(151.19,458.61);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (151.19,452.94) {$h$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (150.17,453.18) --
	(158.44,453.18);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.75,451.58) --
	(154.75,454.65);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (154.75,450.27) {$\sigma$};
\definecolor{drawColor}{RGB}{0,195,0}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (199.83,488.43) --
	(200.35,488.43);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (200.09,487.96) --
	(200.09,488.88);
\definecolor{drawColor}{RGB}{0,195,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (200.09,485.52) {$\kappa$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (119.54,419.45) --
	(125.87,419.45);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (122.97,413.25) --
	(122.97,424.13);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (122.97,416.23) {$p$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (156.29,461.77) --
	(162.87,461.77);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (159.86,457.79) --
	(159.86,465.07);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (159.86,457.74) {$L$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (154.77,462.26) --
	(155.59,462.26);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (155.19,457.82) --
	(155.19,465.86);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (155.19,458.22) {$r$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (111.36,420.07) --
	(124.02,420.07);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (118.72,413.64) --
	(118.72,424.87);
\definecolor{drawColor}{RGB}{0,219,171}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.16] at (118.72,416.04) {$h$};
\definecolor{drawColor}{RGB}{0,219,171}

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (125.89,409.29) --
	(132.73,409.29);

\path[draw=drawColor,draw opacity=0.60,line width= 0.4pt,line join=round,line cap=round] (129.61,403.87) --
	(129.61,413.52);
\definecolor{drawColor}{RGB}{0,219,171}
